\thetitle

### 2021-04-30 writing/mutate-benchmarks.tex
Try to note assumptions about benchmarks typability and determinism

\item vary in size, complexity and purpose;

\item have a decent number of modules and a variety of module dependency graphs
 (because mixing of typed and untyped code in Typed Racket takes place at the
 module level);

>>>>

\item vary in size, complexity and purpose;\footnote{A finer point worth noting is that since the rational programmer assumes observable changes in program behavior are due to its actions, the programs should be deterministic.}

\item have a decent number of type-able modules and a variety of module dependency graphs
 (because mixing of typed and untyped code in Typed Racket takes place at the
 module level);
